Tabular Constraint Learning

### 2016-04-12 Paper/ECAI/tabular.tex
Table WIP

\begin{table*}
  \centering
  \begin{tabular}{lcc}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    ALLDIFFERENT(X) & & \\
    X = Y & & \\
    FK $\rightarrow$ PK & & \\
    % TODO check out
    R = LOOKUP-PRODUCT(FV, FK=PK, PV) & & \\
    FV = FUZZY-LOOKUP(FK, PK, PV) & & \\
    FV = LOOKUP(FK, PK, PV) & & \\
    PERMUTATION(X) & & \\
    R = O1 * O2 & & \\
    R = PROJECT(P) & & \\
     Y = RANK(X)   & & \\
    A = PREV(A) + P - N & & \\
    SERIES(X) & & \\
    Y = SUM(X, col) & & \\
    Y = SUM(X, row) & & \\
    R = SUMIF(FK=PK, V) & & \\
    R = SUMPRODUCT(O1, O2) & & \\

>>>>

\begin{table*}
  \centering
  \begin{tabular}{ccc}
    \textbf{\CName} & \textbf{\CSignature} & \textbf{\CFunction}\\
    ALLDIFFERENT(X) & X is integer or textual & All elements in X are different \\
    %X = Y & & \\
    FK $\rightarrow$ PK & FK and PK have the same type; they originate from different tables and PK is all-different & all values in FK exist in PK \\
    % TODO check out
    R = LOOKUP-PRODUCT(FV, FK=PK, PV) & & \\
    FV = FUZZY-LOOKUP(FK, PK, PV) & & \\
    FV = LOOKUP(FK, PK, PV) & & \\
    PERMUTATION(X) & & \\
    R = O1 * O2 & & \\
    R = PROJECT(P) & & \\
     Y = RANK(X) & & \\
    A = PREV(A) + P - N & A, P and N have the same length and their length is at least 2 & *\\
    SERIES(X) & & \\
    Y = SUM(X, col) & & Y is the result of summing each column in X \\
    Y = SUM(X, row) & & Y is the result of summing each row in X \\
    R = SUMIF(FK=PK, V) & & \\
    R = SUMPRODUCT(O1, O2) & & \\
